---
title: "Models"
author: "Amogh Patil"
format: html
execute:
  echo: false
---

Using data from a YouGov poll of 1,559 US adult citizens, conducted March 10 - 12, 2024, we are trying to find what % of voters will vote for Biden in 2024. The proportion might change until election day. The number is around 42%, but it will vary by around 5%. Because no algorithm is perfect, there will be some uncertanty. However, conducting more polls may help narrow the results.

We will use this formula:
$$ biden_i =  \mu + \epsilon_i $$

```{r}
#| label: setup
#| message: FALSE
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)

```

```{r}
#| label: model
#| cache: true
fit_bern<-brm(formula = biden ~ 1, data = poll_data, family = bernoulli(), refresh = 0, silent = 2, seed = 9)
```

```{r}
tbl_regression(fit_bern, intercept=TRUE)
```

```{r}
#| label: plot
fit_bern|>
  add_epred_draws(ndata)|>
    select(.epred)|>
      ggplot(aes(x=.epred, y=after_stat(count/sum(count))))+
      geom_density()+
      scale_x_continuous(labels = scales::percent_format())+
      scale_y_continuous(labels = scales::percent_format())+
      labs(title="Posterior Distribution for $ \rho $",
           subtitle="There is a 95% chance for a value between XX and XX",
           x="Proportion,$ \rho $,of red beads in Urn",
           y="Probability")
```

